Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-27 ECCV/paper.tex
Added introduction about fiducials and relevant references.

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02}, we have designed a fiducial
that may be thought of as a binary code. It contains concentric white rings of
equal widths on a black background with a blurred border. Our fiducial detection
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion. We will show through experimental
validation that our fiducial works better than popular fiducials such as
ARTag under signifacant motion blur.

@@

\section{Introduction}
A fiducial marker or simply a fiducial is an synthetic object placed in the
scene, which can provide additional information about the environment.

Low cost quadcopters such as AR Drone are very unstable which causes non-uniform
motion resulting lot of motion blur in captured images. Also, as image transfer
is done through wireless media using User Datagram Protocol (UDP), there is
possibility of missing intermediate frames . It results in lower frame rate
(around 15 frames per second (FPS)) instead of normal rate of 30 FPS. This
frequent dropping of frames may cause drastic change in position of object in
successive frames. Thus, performance of traditional tracking methods is not
satisfactory for tracking through quadcopters. Our aim is to design a fiducial
which we will be able to track under significant amount of motion blur and is
robust in terms of drastic change in its position in successive frames.

@@

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}

@@

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02}, we have designed a fiducial
that may be thought of as a binary code. It contains concentric white rings of
equal widths on a black background with a blurred border. Our fiducial detection
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion. The algorithm finds this
direction in a simple but accurate way. Then, we find ``signature'' of our
fiducial along this direction and further classify it to find the actual code
embedded in the fiducial. We will show through experimental validation that our
fiducial works better than popular fiducials such as ARTag under signifacant motion blur.

@@

\section{Introduction}
A fiducial marker or simply a fiducial is an synthetic object placed in the
scene, which can provide additional information about the environment. Sometimes
naturally available features in a scene may be used as replacement to fiducials.
But, natural features may not be available always and quality cannot be
guranteed in every scene. So, results are not satisfactory in uncontrolled
environment and hence use of such features is limited. Artificial fiducials are
widely used in Augmented Reality(AR)\cite{Zhang:2002}\cite{Dorfmuller99}
applications, vision based navigation of robots\cite{Davison:2007} etc.

Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
in various tracking activities (e.g. aerial surveillance, search and rescue
operations etc.).Low cost quadcopters such as AR Drone are very unstable which
causes non-uniform motion resulting lot of motion blur in captured images.
Also, as image transfer is done through wireless media using User Datagram
Protocol (UDP), there is possibility of missing intermediate frames . It
results in lower frame rate (around 15 frames per second (FPS)) instead of
normal rate of 30 FPS. This frequent dropping of frames may cause drastic
change in position of object in successive frames. Thus, performance of
traditional tracking methods is not satisfactory for tracking through
quadcopters. Our aim is to design a fiducial which we will be able to track
under significant amount of motion blur and is robust in terms of drastic
change in its position in successive frames.

@@

%\begin{tabular}

%\end{tabular}
Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.
